make STEAM clear

### 2019-12-01 Journal/20191125.tex
let's call it a day

\section{preface}
\label{sec:orgb73e917}

@@

\section{15:39 Basics of signals and systems}
\label{sec:org023432e}

@@

\section{definition of signals and systems}
\label{sec:org0083078}

Fist give the definition of singal then system.
\subsection{definition of signals}
\label{sec:orgc5b8c56}

@@

A discrete-time signal is a sequence of values of interest, where the integer
index can be thought of as a time index, and the values in the sequence
represent some physical quantity of interest. Because many discrete-time signals
arise as equally-spaced samples of a continuous-time signal, it is often more
convenient to think of the index as the "sample number".
\subsection{examples of signals}
\label{sec:org9e7ff00}

\subsubsection{ECG signal}
\label{sec:org6aa518f}

\subsubsection{Speech signal}
\label{sec:org4599249}

\subsubsection{Image}
\label{sec:orgb9ba77a}

\subsection{definition of systems}
\label{sec:org50a98a3}

@@

In general, two types of tools related with continuous-time signals and
discrete-time signals will be covered. For example, for the continuous-time
signals we have Fourier Transform and Laplace transform whereas for the
discrete-time signals we have discrete time Fourier Transforms and Z-transform.
Living in a digitized world, I use discrete-time signals related tools more
often than the continuous-time counterpart. Now, it seems that the
continuous-time signals only exists before analog-digital converter (ADC).
However, to analyze a signal, the continuous-time related tools provide a more
mathematical and theoretical way. So during the learning and teaching signals
and systems, I will cover both continuous-time and discrete-time topics and give
as many details about both realms as I can. Fortunately, we have sampling theory
and ADC, we can easily move from continuous-time world to discrete-time world .
Most of the conclusions we draw from the continuous-time world will apply in the
discrete-time world with no or only a little modification.
\subsection{examples of systems}
\label{sec:org371aacc}

\subsubsection{ECG system}
\label{sec:orge20180e}

\subsubsection{Voice recording system}
\label{sec:org4bc4f48}

\subsubsection{Camera Systems}
\label{sec:org36b0296}

\section{summary of chapter 1}
\label{sec:org273cc92}

@@

\section{references}
\label{sec:orgc602a8b}

@@

\item Dr Wickert's website \href{http://www.eas.uccs.edu/\~mwickert/}{Dr. Wickert's Info Center}  has quite a lot resources
for a engineering student.
\end{enumerate}
\section{architecture of each video}
\label{sec:org64de00f}

\begin{enumerate}
\item every video will contain several topics but the mathematical derivation will
not be so all-inclusive. More details will given as posts in this site for whom
may be interested. So you can grab the overall structure at first then
reinforce the it with more bricks.
\item For each video, only several key points will be explained. I don't want the
video make you feel boring or tired.
\item A piece of suggestion for the serious learner: watch the video twice or even
more. Most often, even some concepts which are relatively simple at first
look hide some deep relation with other concepts. The obscure relation will
not be illustrated in the video if it does not affect the understanding of
current object.
\end{enumerate}
\end{document}

>>>>

\section{Wednesday, 11/27/19}
\label{sec:org7ec480d}
\subsection{19:20 academic theme}
\label{sec:orgc626325}
\subsection{use power thesaurus.el}
\label{sec:orgd065b2d}

\href{https://github.com/SavchenkoValeriy/emacs-powerthesaurus}{SavchenkoValeriy/emacs-powerthesaurus: Powerthesaurus integration for Emacs}

Emacs-powerthesaurus is a simple plugin to integrate Emacs with amazing
powerthesaurus.org

\section{Saturday, 11/30/19}
\label{sec:org5c14c91}

\section{Sunday, 12/01/19}
\label{sec:org4ace420}
\subsection{introduction to signal and system}
\label{sec:orgabba3dd}
\subsubsection{preface}
\label{sec:org8b47609}

@@

\subsubsection{15:39 Basics of signals and systems}
\label{sec:org42860fe}

@@

\subsubsection{definition of signals and systems}
\label{sec:org785eae1}

Fist give the definition of singal than system.
\begin{enumerate}
\item definition of signals
\label{sec:org9e28d14}

@@

A discrete-time signal is a sequence of values of interest, where the integer
index can be thought of as a time index, and the values in the sequence
represent some physical quantity of interest. Because many discrete-time signals
arise as equally-spaced samples of a continuous-time signal, it is often more
convenient to think of the index as the "sample number".
\item examples of signals
\label{sec:orge975172}

\begin{enumerate}
\item ECG signal
\label{sec:orgc8f647d}

\item Speech signal
\label{sec:org934f365}

\item Image
\label{sec:org28628c9}
\end{enumerate}

\item definition of systems
\label{sec:orgce71be0}

@@

In general, two types of tools related with continuous-time signals and
discrete-time signals will be covered. For example, for the continuous-time
signals we have Fourier Transform and Laplace transform whereas for the
discrete-time signals we have discrete time Fourier Transforms and Z-transform.
Living in a digitized world, I use discrete-time signals related tools more
often than the continuous-time counterpart. Now, it seems that the
continuous-time signals only exists before analog-digital converter (ADC).
However, to analyze a signal, the continuous-time related tools provide a more
mathematical and theoretical way. So during the learning and teaching signals
and systems, I will cover both continuous-time and discrete-time topics and give
as many details about both realms as I can. Fortunately, we have sampling theory
and ADC, we can easily move from continuous-time world to discrete-time world .
Most of the conclusions we draw from the continuous-time world will apply in the
discrete-time world with no or only a little modification.
\item examples of systems
\label{sec:org4f5abb0}

\begin{enumerate}
\item ECG system
\label{sec:org705072e}

\item Voice recording system
\label{sec:orga139225}

\item Camera Systems
\label{sec:org0ec4a51}
\end{enumerate}
\end{enumerate}

\subsubsection{summary of chapter 1}
\label{sec:org9c0f4d4}

@@

\subsubsection{references}
\label{sec:org63c4515}

@@

\item Dr Wickert's website \href{http://www.eas.uccs.edu/\~mwickert/}{Dr. Wickert's Info Center}  has quite a lot resources
for a engineering student.
\end{enumerate}
\subsubsection{architecture of each video}
\label{sec:org29e6fbc}

\begin{enumerate}
\item every video will contain several topics but the mathematical derivation will
not be so all-inclusive. More details will given as posts in this site for whom
may be interested. So you can grab the overall structure at first then
reinforce the it with more bricks.
\item For each video, only several key points will be explained. I don't want the
video make you feel boring or tired.
\item A piece of suggestion for the serious learner: watch the video twice or even
more. Most often, even some concepts which are relatively simple at first
look hide some deep relation with other concepts. The obscure relation will
not be illustrated in the video if it does not affect the understanding of
current object.
\end{enumerate}

\subsection{08:05 introduction to signal and system (ver2)}
\label{sec:org0a474bf}

As a basic "language" for engineering students, signals and systems appears in a
variety of fields which can be communications, aeronautics and astronautics,
circuit design, acoustics, seismology, biomedical engineering, energy generation
and distribution systems, chemical process control, and speech processing. The
tools developed in this course will play an important role in the future for
engineering students.

Before we give some official definitions of signals and systems, let's dive into
some examples.
\begin{center}
\includegraphics[width=0.6\textwidth]{../../img/icon-512.png}
\end{center}
\end{document}

### 2019-12-01 mstemc/mstemc.tex
let's call it a day

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
\author{Eason Zhang}
\date{\today}
\title{make STEM clear}
\hypersetup{
 pdfauthor={Eason Zhang},
 pdftitle={make STEM clear},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{Videos}
\label{sec:org998bcda}

\section{Posts}
\label{sec:org3d17ce5}

\section{Projects}
\label{sec:orgc54445f}

\subsection{my workflow of creating a video}
\label{sec:orgf0ee6dd}
During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:org0c108f2}

@@

\begin{enumerate}
\item program and debug
\label{sec:org1ff6423}

@@

\item Org mode - journalize your work
\label{sec:org12d2f61}

@@

\item Org mode - get things done
\label{sec:org5ad0d61}

\item Org mode - write a diary
\label{sec:org32d0506}

\item Org mode - export your Org file
\label{sec:org4d11418}

\item program and debug
\label{sec:orgeef06a2}

\item writing latex
\label{sec:org9ac1f7a}
\item org-journal
\label{sec:orga432c48}

@@

\item ox-hugo
\label{sec:orgf65906e}

@@

\subsubsection{Hugo}
\label{sec:orgc828f72}

@@

\subsubsection{manim}
\label{sec:orgea6a849}

\subsubsection{blender}
\label{sec:orge06e6d2}

\section{Courses}
\label{sec:org7e36065}
\end{document}

>>>>

% Intended LaTeX compiler: xelatex
\documentclass[koma,letterpaper,captions=tableheading,ctex,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
                  \usepackage{ctex}
                  \usepackage{tikztheorem}
\author{Eason Zhang}
\date{\today}
\title{make STEAM clear}
\hypersetup{
 pdfauthor={Eason Zhang},
 pdftitle={make STEAM clear},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{Videos}
\label{sec:orgc58e4f7}

\section{Posts}
\label{sec:orgb1332b6}

\section{Projects}
\label{sec:orgffac4f6}

\subsection{my workflow of creating a video}
\label{sec:orgb86eaa9}
 中文 你好
During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:orgadf0dac}

@@

\begin{enumerate}
\item program and debug
\label{sec:org954f607}

@@

\item Org mode - journalize your work
\label{sec:org0cf6dc5}

@@

\item Org mode - get things done
\label{sec:orgd228748}

\item Org mode - write a diary
\label{sec:orgd304635}

\item Org mode - export your Org file
\label{sec:orgf2a7087}

\item program and debug
\label{sec:org81e3cf7}

\item writing latex
\label{sec:orgb6b215c}
\item org-journal
\label{sec:org7fba657}

@@

\item ox-hugo
\label{sec:org5bd6c0b}

@@

\subsubsection{Hugo}
\label{sec:org142d742}

@@

\subsubsection{manim}
\label{sec:orga5a3f16}

\subsubsection{blender}
\label{sec:org41eda2c}

\section{Courses}
\label{sec:org7835e17}
\end{document}
